Adaptative neigbouring methods applied to telephonic base stations

### 2024-08-20 article.tex
Modification emplacement images et indentations

\section{Databases}
Several databases have been used in order to test the different aspects of the methods. However, one of
them is directly necessary to the method itself.

@@

The fields that are being used here are described in Table~\ref{table:data_columns}. [expliquer qu'il y x colonnes mais qu'on utilise que elles]

@@

\begin{table}[!b]
    \centering
    \caption{Number of \acrfull{bs} equipped, at least, with $x$G, by provider}
    \label{table:techno_numbers}
    \begin{tabular}{cccccc}
        \toprule
        \textbf{Technology} & \textbf{Bouygues} & \textbf{Free} & \textbf{Orange} & \textbf{SFR} & \textbf{Total} \\
        \cmidrule(lr){1-6}
        \textbf{2G} & 21710 & 0 & 18835 & 20093 & 60638 \\
        \textbf{3G} & 26294 & 25934 & 29748 & 25777 & 107753 \\
        \textbf{4G} & 26231 & 25847 & 30440 & 25881 & 108399 \\
        \textbf{5G} & 11271 & 18607 & 8794 & 10968 & 49640 \\
        \textbf{Total} & 26331 & 25949 & 30540 & 26018 & 108838 \\
        \bottomrule
    \end{tabular}
\end{table}

\begin{figure}[!t]
    \centering
    \boxed{\includegraphics[width=2.5in]{images/data_analysis/with_techno.png}}
    \caption{Breakdown, by operator, of the number of sites containing a given technology}
    \label{fig:data_technos}
\end{figure}

\begin{table}[!b]
    \centering
    \caption{Description of the main database columns used in the experiments}
    \label{table:data_columns}
    \begin{tabular}{ll}
        \toprule
        \textbf{Column} & \textbf{Description} \\
        \cmidrule(lr){1-2}
        \textsl{id\_station\_anfr} & \acrshort{anfr} \acrshort{bs} ID \\ 
        \textsl{nom\_op} & Name of the provider \\
        \textsl{x, y, latitude, longitude} & Base station coordinates \\ 
        \textsl{nom\_reg, nom\_dep, nom\_com} & Additional location information \\  
        \textsl{site\_2g, 3g, 4g, 5g} & Technology used by the \acrshort{bs} \\ 
        \bottomrule
    \end{tabular}
\end{table}

@@

Finally, in order to simplify viewing, we will apply our neighbouring only on the Normandie region just because this is where we live.
\section{Reminder on existing methods}
\subsection{Finding potential neighbours}
\noindent When we are looking for neighbours, we need, at first, a list of potential neighbours for each point.
For that, we will construct a neigbouring graph $G = (P, U)$ where $P$ is the set of all points and each edge in $U$ represents a neighbouring relation.

@@

\begin{figure}[!t]
    \centering
    \boxed{\includegraphics[width=1.25in]{images/illus_graphs/Delaunay_circumcircles_vectorial.png}}
    \boxed{\includegraphics[width=1.25in]{images/illus_graphs/Delaunay_Voronoi.png}}
    \caption{Example of a Delaunay triangulation (in black) and Voronoi diagram (in red)}
    \label{fig:del_tri}
\end{figure}

@@

\subsection{Finding real neighbours}
\noindent For the purpose of our experiments, i.e. finding \acrshort{bs} neighbours, the previously presented methods are not sufficient to find real neighbours.
As a consequence, some neighbouring connexions needs to be suppressed \cite{patent_neighs}.
\subsubsection{Distance criterion\cite{patent_neighs}}
A \acrshort{bs} does not have an infinite coverage area.
As a consequence, each edge in $U$ that is longer than a certain value, called \emph{max\_distance}, is suppressed.

@@

\subsection{Density-based clustering methods}
\noindent Although the filtering methods are providing good results, it is still not enough.
Therefore, we will modify those criteria to take in account the variations of \acrshort{bs} density. Thus, we need some measurement of this density.

@@

\subsection{Measurement of \acrshort{bs} density}
\noindent Places with a high population also have a high density of base stations. In fact, each base station can only support a certain
load of users.

>>>>

\section{Databases}
\noindent Several databases have been used in order to test the different aspects of the methods. However, one of
them is directly necessary to the method itself.

@@

The fields that are being used here are described in Table~\ref{table:data_columns}. [expliquer qu'il y x colonnes mais qu'on utilise que elles]
\begin{table}[!b]
    \centering
    \caption{Description of the main database columns used in the experiments}
    \label{table:data_columns}
    \begin{tabular}{ll}
        \toprule
        \textbf{Column} & \textbf{Description} \\
        \cmidrule(lr){1-2}
        \textsl{id\_station\_anfr} & \acrshort{anfr} \acrshort{bs} ID \\ 
        \textsl{nom\_op} & Name of the provider \\
        \textsl{x, y, latitude, longitude} & Base station coordinates \\ 
        \textsl{nom\_reg, nom\_dep, nom\_com} & Additional location information \\  
        \textsl{site\_2g, 3g, 4g, 5g} & Technology used by the \acrshort{bs} \\ 
        \bottomrule
    \end{tabular}
\end{table}

@@

\begin{table}[!t]
    \centering
    \caption{Number of \acrfull{bs} equipped, at least, with $x$G, by provider}
    \label{table:techno_numbers}
    \begin{tabular}{cccccc}
        \toprule
        \textbf{Technology} & \textbf{Bouygues} & \textbf{Free} & \textbf{Orange} & \textbf{SFR} & \textbf{Total} \\
        \cmidrule(lr){1-6}
        \textbf{2G} & 21710 & 0 & 18835 & 20093 & 60638 \\
        \textbf{3G} & 26294 & 25934 & 29748 & 25777 & 107753 \\
        \textbf{4G} & 26231 & 25847 & 30440 & 25881 & 108399 \\
        \textbf{5G} & 11271 & 18607 & 8794 & 10968 & 49640 \\
        \textbf{Total} & 26331 & 25949 & 30540 & 26018 & 108838 \\
        \bottomrule
    \end{tabular}
\end{table}

\begin{figure}[!b]
    \centering
    \boxed{\includegraphics[width=2.5in]{images/data_analysis/with_techno.png}}
    \caption{Breakdown, by operator, of the number of sites containing a given technology}
    \label{fig:data_technos}
\end{figure}

@@

Finally, in order to simplify viewing, we will apply our neighbouring only on the Normandie region just because this is where we live.
\section{Reminder on existing methods}
\subsection{Finding potential neighbours}
When we are looking for neighbours, we need, at first, a list of potential neighbours for each point.
For that, we will construct a neigbouring graph $G = (P, U)$ where $P$ is the set of all points and each edge in $U$ represents a neighbouring relation.

@@

\begin{figure}[!b]
    \centering
    \boxed{\includegraphics[width=1.25in]{images/illus_graphs/Delaunay_circumcircles_vectorial.png}}
    \boxed{\includegraphics[width=1.25in]{images/illus_graphs/Delaunay_Voronoi.png}}
    \caption{Example of a Delaunay triangulation (in black) and Voronoi diagram (in red)}
    \label{fig:del_tri}
\end{figure}

@@

\subsection{Finding real neighbours}
For the purpose of our experiments, i.e. finding \acrshort{bs} neighbours, the previously presented methods are not sufficient to find real neighbours.
As a consequence, some neighbouring connexions needs to be suppressed \cite{patent_neighs}.
\subsubsection{Distance criterion\cite{patent_neighs}}
A \acrshort{bs} does not have an infinite coverage area.
As a consequence, each edge in $U$ that is longer than a certain value, called \emph{max\_distance}, is suppressed.

@@

\subsection{Density-based clustering methods}
Although the filtering methods are providing good results, it is still not enough.
Therefore, we will modify those criteria to take in account the variations of \acrshort{bs} density. Thus, we need some measurement of this density.

@@

\subsection{Measurement of \acrshort{bs} density}
Places with a high population also have a high density of base stations. In fact, each base station can only support a certain
load of users.
